Stable individual differences in strategies within, but not between, visual search tasks

### 2019-10-29 Manuscript/manuscript.tex
fixed citation

Eye movement strategies have also been shown to be an important source of individual differences in visual search efficiency. \cite{nowakowska2017} designed a simple search paradigm to discriminate between optimal \cite{najemnik-geisler2008} and stochastic  \cite{clarke2016} search strategies. Participants searched through arrays of line segments (Figure \ref{fig:exampleStimuli}) arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous). This meant that targets appearing on the homogeneous side were highly salient, while targets on the heterogeneous side were harder to find. The optimal strategy here is to search the heterogeneous half, as targets on the homogeneous side can be detected with peripheral vision. We will refer to this paradigm as the Split-Half Line Segment task (SHLS). Some participants searched the displays near optimally, but others carried out strategies counter to this, failing to even match the performance of the stochastic searcher. The degree to which participants made saccades in line with the optimal search strategy was strongly correlated with the speed of their search. A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia \cite{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed. It is therefore not possible to conclude whether optimal or stochastic models better describe search without first explaining individual variability.

>>>>

Eye movement strategies have also been shown to be an important source of individual differences in visual search efficiency. Nowakowska, Clarke & Hunt \citeyear{nowakowska2017} designed a simple search paradigm to discriminate between optimal \cite{najemnik-geisler2008} and stochastic  \cite{clarke2016} search strategies. Participants searched through arrays of line segments (Figure \ref{fig:exampleStimuli}) arranged such that those on one side of the display all had a very similar orientation (homogeneous), while those on the other side had higher variance (heterogeneous). This meant that targets appearing on the homogeneous side were highly salient, while targets on the heterogeneous side were harder to find. The optimal strategy here is to search the heterogeneous half, as targets on the homogeneous side can be detected with peripheral vision. We will refer to this paradigm as the Split-Half Line Segment task (SHLS). Some participants searched the displays near optimally, but others carried out strategies counter to this, failing to even match the performance of the stochastic searcher. The degree to which participants made saccades in line with the optimal search strategy was strongly correlated with the speed of their search. A related version of this paradigm has been used in research investigating eye movement strategies in response to (simulated) hemianopia \cite{nowakowska2016,nowakowska2018}, with similar conclusions: the full spectrum of individual differences in strategy was observed. It is therefore not possible to conclude whether optimal or stochastic models better describe search without first explaining individual variability.
